Follow-up Samples

### 2017-02-20 submission/manuscript_outline_20161024.Rmd
abstract corrections

**Results:** The bacterial microbiome in pre and post surgery samples for the adenoma group were more similar to each other than the carcinoma group (P-value `r ifelse(change_summary['thetayc', 'Pvalue'] < 0.05, paste("<"), paste(">"))` 0.05).  There was no difference for either the adenoma or carcinoma group in the relative abundance of any OTU between the pre and post lesion removal (P-value `r ifelse(min(filter(all_OTU_pair_wilcox, analysis == "ALL")[, 'BH_corrected']) < 0.05, paste("<"), paste(">"))` 0.05).  A model built to classify model built to classify lesion had an AUC range of `r format(min(lesion_AUC_run_summary$ROC), digits = 3)` - `r format(max(lesion_AUC_run_summary$ROC), digits = 3)` while a model built to classify initial versus follow up samples had an AUC range of `r format(min(IF_AUC_run_summary$ROC), digits = 3)` - `r format(max(IF_AUC_run_summary$ROC), digits = 3)`.  The post removal sample for both models had a decrease in the positive probability for either lesion or initial sample (P-value `r ifelse(filter(all_probs_paired_wilcox, model_type == "red_lesion" & comparison =="lesion")[, "BH_correction"] < 0.05, paste("<"), paste(">"))` 0.05).  The lesion model used a total of `r length(lesion_top10_varsMDA$variable)` variables while the initial sample model used a total of `r length(IF_top10_varsMDA$variable)` variables.  A total of `r length(common_vars_summary$otu)` OTUs were common to both models with the majority of these classifying to commensal bacteria (e.g. *`r filter(common_vars_summary, otu == "Otu000028")[, "lowest_ID"]`*, *`r filter(common_vars_summary, otu == "Otu000018")[, "lowest_ID"]`*, *`r filter(common_vars_summary, otu == "Otu000009")[, "lowest_ID"]`*, and *`r filter(common_vars_summary, otu == "Otu000005")[, "lowest_ID"]`*).

>>>>

**Results:** The bacterial microbiome in pre and post lesion removal samples for the adenoma group were more similar to each other than the carcinoma group (P-value `r ifelse(change_summary['thetayc', 'Pvalue'] < 0.05, paste("<"), paste(">"))` 0.05).  There was no difference for either the adenoma or carcinoma group in the relative abundance of any OTU between the pre and post lesion removal (P-value `r ifelse(min(filter(all_OTU_pair_wilcox, analysis == "ALL")[, 'BH_corrected']) < 0.05, paste("<"), paste(">"))` 0.05).  A model built to classify model built to classify lesion had an AUC range of `r format(min(lesion_AUC_run_summary$ROC), digits = 3)` - `r format(max(lesion_AUC_run_summary$ROC), digits = 3)` while a model built to classify initial versus follow up samples had an AUC range of `r format(min(IF_AUC_run_summary$ROC), digits = 3)` - `r format(max(IF_AUC_run_summary$ROC), digits = 3)`.  Follow up samples had a decrease in the positive probability (P-value `r ifelse(filter(all_probs_paired_wilcox, model_type == "red_lesion" & comparison =="lesion")[, "BH_correction"] < 0.05, paste("<"), paste(">"))` 0.05).  This decrease in positive probability was also observed for the initial sample model (P-value `r ifelse(filter(all_probs_paired_wilcox, model_type == "red_IF" & comparison =="lesion")[, "BH_correction"] < 0.05, paste("<"), paste(">"))` 0.05).  The lesion model used a total of `r length(lesion_top10_varsMDA$variable)` variables while the initial sample model used a total of `r length(IF_top10_varsMDA$variable)` variables.  A total of `r length(common_vars_summary$otu)` OTUs were common to both models with the majority of these classifying to commensal bacteria (e.g. *`r filter(common_vars_summary, otu == "Otu000028")[, "lowest_ID"]`*, *`r filter(common_vars_summary, otu == "Otu000018")[, "lowest_ID"]`*, *`r filter(common_vars_summary, otu == "Otu000009")[, "lowest_ID"]`*, and *`r filter(common_vars_summary, otu == "Otu000005")[, "lowest_ID"]`*).

### 2017-02-20 submission/manuscript_outline_20161024.tex
abstract corrections

\textbf{Results:} The bacterial microbiome in pre and post surgery
samples for the adenoma group were more similar to each other than the
carcinoma group (P-value \textless{} 0.05). There was no difference for
either the adenoma or carcinoma group in the relative abundance of any
OTU between the pre and post lesion removal (P-value \textgreater{}
0.05). A model built to classify model built to classify lesion had an
AUC range of 0.811 - 0.866 while a model built to classify initial
versus follow up samples had an AUC range of 0.641 - 0.805. The post
removal sample for both models had a decrease in the positive
probability for either lesion or initial sample (P-value \textless{}
0.05). The lesion model used a total of 53 variables while the initial
sample model used a total of 70 variables. A total of 23 OTUs were
common to both models with the majority of these classifying to
commensal bacteria (e.g. \emph{Bacteroides}, \emph{Clostridiales},
\emph{Blautia}, and \emph{Ruminococcaceae}).

>>>>

\textbf{Results:} The bacterial microbiome in pre and post lesion
removal samples for the adenoma group were more similar to each other
than the carcinoma group (P-value \textless{} 0.05). There was no
difference for either the adenoma or carcinoma group in the relative
abundance of any OTU between the pre and post lesion removal (P-value
\textgreater{} 0.05). A model built to classify model built to classify
lesion had an AUC range of 0.811 - 0.866 while a model built to classify
initial versus follow up samples had an AUC range of 0.641 - 0.805.
Follow up samples had a decrease in the positive probability (P-value
\textless{} 0.05). This decrease in positive probability was also
observed for the initial sample model (P-value \textless{} 0.05). The
lesion model used a total of 53 variables while the initial sample model
used a total of 70 variables. A total of 23 OTUs were common to both
models with the majority of these classifying to commensal bacteria
(e.g. \emph{Bacteroides}, \emph{Clostridiales}, \emph{Blautia}, and
\emph{Ruminococcaceae}).
